Improving Code Completion in Pharo\\Using N-gram Language Models

### 2020-05-15 ACM/abstract.tex
updated formatting
updated the template in accordance with the most recent guidelines

\documentclass[format=sigconf]{acmart}

@@

>>>>

\documentclass[sigconf,screen]{acmart}

@@

\copyrightyear{2020}
\acmYear{2020}
\setcopyright{acmcopyright}\acmConference[ '20]{Conference Companion of the 4th International Conference on the Art, Science, and Engineering of Programming}{March 23--26, 2020}{Porto, Portugal}
\acmBooktitle{Conference Companion of the 4th International Conference on the Art, Science, and Engineering of Programming ( '20), March 23--26, 2020, Porto, Portugal}
\acmPrice{15.00}
\acmDOI{10.1145/3397537.3398483}
\acmISBN{978-1-4503-7507-8/20/07}
